Empty Homes V1

### 2017-06-05 EmptyHomesV1.Rmd
Bootstrapped ratios
Created bootstrapped ratios, the results are unexpected and need to be checked.

t.test(v,alternative = "greater")

@@

test3 <- Chelseainfo %>% 
  group_by(Admin_ward_code) %>%
  summarise_all(funs(first)) %>%
  select(Admin_ward_code, WardLowUse, WardHomes) %>%
  left_join(., test, "Admin_ward_code") %>%
  mutate(LowUseClass = WardLowUse*WardPerc,
         HomesClass = WardHomes*WardPerc) %>%
  group_by(class) %>%
  summarise(LowUseClass = sum(LowUseClass),
            HomesClass = sum(HomesClass)) %>%
  filter(complete.cases(.)) %>%
  mutate(PercOfLowUse = LowUseClass/sum(LowUseClass),
         PercOfHomes = HomesClass/sum(HomesClass),
         PercofClass = LowUseClass/HomesClass)

#Percentage over and under of what would be expected if buying was random
#The differences suggest that people are buying more expensive homes when there is no plan to live in them.
round(test3$LowUseClass/(sum(test3$LowUseClass)*test3$PercOfHomes),2)
```

>>>>

#the data is not normal
plot(density(v))
#this prob not valid
t.test(v,alternative = "greater")

#do a bootstrapped mean to see if it is greater than the mean of the homes overall.
set.seed(1258)
samps <-10000

bootres <- 1:samps %>% map(~data.frame(res =sample(v, length(v), replace = T))) %>%
  bind_cols()

sum(colMeans(bootres)>0)/samps

plot(density(colMeans(bootres+ChelMeanPrice)))

#%>% setNames(paste0("samp",.x))

@@

test3 <- Chelseainfo %>% 
  group_by(Admin_ward_code) %>%
  summarise_all(funs(first)) %>%
  select(Admin_ward_code, WardLowUse, WardHomes) %>%
  left_join(., test, "Admin_ward_code") %>%
  mutate(LowUseClass = WardLowUse*WardPerc,
         HomesClass = WardHomes*WardPerc) %>%
  group_by(class) %>%
  summarise(LowUseClass = sum(LowUseClass),
            HomesClass = sum(HomesClass)) %>%
  filter(complete.cases(.)) %>%
  mutate(PercOfLowUse = LowUseClass/sum(LowUseClass),
         PercOfHomes = HomesClass/sum(HomesClass),
         PercofClass = LowUseClass/HomesClass,
         `Expected Homes` = PercOfHomes*sum(LowUseClass),
         `Actual Homes` = PercOfLowUse*sum(LowUseClass))

sum(test3$LowUseClass)*test3$PercOfHomes

#Percentage over and under of what would be expected if buying was random
#The differences suggest that people are buying more expensive homes when there is no plan to live in them.
round(test3$LowUseClass/(sum(test3$LowUseClass)*test3$PercOfHomes),2)

ggplot(test3, aes(x= class, y = PercOfHomes*100)) +geom_bar(stat = "identity") + 
  labs(title = "Distribution probability of homes in each class", y = "Percentage")

test3 %>%
  select(class, `Expected Homes`, `Actual Homes`) %>%
  gather(key = "Type" , value = "Number", -class) %>%
  ggplot(., aes(x= class, y = Number, fill = Type)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Expected Number of low-use homes in each class")

test3 %>%
  mutate(`Percentage Difference` = (`Actual Homes`/`Expected Homes`)*100-100) %>%
  ggplot(., aes(x= class, y = `Percentage Difference`)) +
  geom_bar(stat = "identity") +
  labs(title = "Percentage difference between expected number of homes per class and actual")+
  coord_cartesian(ylim=c(-20,20))

#Chelsea Bootstrapped ratios

```{r}
 ChelPrice <- prices %>% 
  filter( Admin_district_code =="E09000020") %>%
  select(lsoa11cd, Price =X2) %>%
  mutate(class = cut(Price, c(0,  490,      750,   2000, 12000, Inf)*10^3, 
            labels =     c("Lower", "Mid", "Upper", "Prime", "Super"), 
             right = F))

set.seed(16544)
Chelseastrapped <- ClassStrapper(ChelPrice, sum(Chelseainfo$LowUse))

Chelseastrapped %>% ggplot(., aes(x= class, y = Counts, fill = class)) + geom_boxplot()

test <- unique(ChelPrice$lsoa11cd)%>% 
  map(~ ChelPrice %>% 
        filter(lsoa11cd == .x) %>% 
  ClassStrapper(., sum((filter(Chelseainfo, LSOA_CODE == .x))$LowUse)) %>%
    mutate(class = as.character(class),
           Counts = as.integer(Counts),
           ID = as.integer(ID)) %>%
      setNames(c("class", paste0("Counts", .x) ,"ID"))
  )

ChelseaLSOAstrap <- test %>%  
    Reduce(function(dtf1,dtf2) full_join(dtf1,dtf2, by = c("class", "ID")), .) %>%  
  mutate(Totals = rowSums(.[,c(-1,-3)], na.rm = TRUE)) %>%
select(class, ID, Totals)

test1 <- Chelseastrapped %>% left_join(., ChelseaLSOAstrap, by = c("class", "ID")) %>%
  mutate(ratio = Totals/Counts)

test1 %>% ggplot(., aes(x= class, y = ratio, fill = class)) + geom_boxplot() + 
  labs(title = "Boxplot of bootstrapped Ratios")
